Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-26 Manuscript.Rmd
working on instructions and uploading data to osf

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count
nRegions_DN <- do.call(rbind, studyList_DN) %>% count
nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")

>>>>

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count(X1)
nRegions_DN <- do.call(rbind, studyList_DN) %>% count(X1)
nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")
